evaluating_cv_metric_on_enet_penalization

### 2019-05-22 Scripts/comparing_distance_profiles_using_density_plots.Rmd
editted results scripts

#SMC3
ggplot(all_dist_gm12878, aes(x = Resolution, y = value, fill = y)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(#fill = fill, 
               #colour = line,
               outlier.shape = NA) +
  facet_grid(~ variable) +
  xlab("Resolution") +
  ylab("Log2 Distances") +
  ylim(5,25) +
  scale_fill_discrete(name="Class of Genomic Bin",
                      labels=c("Did not overlap\nw/ flanked TAD boundary",
                               "Overlapped\nw/ flanked TAD boundary")) +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))
```

>>>>

ggplot(all_dist_gm12878, aes(x = Resolution, y = value, fill = y)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(#fill = fill, 
               #colour = line,
               outlier.shape = NA) +
  facet_grid(~ variable) +
  xlab("Resolution") +
  ylab("Log2 Distances") +
  ylim(5,25) +
  scale_fill_discrete(name="Class of Genomic Bin",
                      labels=c("Did not overlap\nw/ flanked TAD boundary",
                               "Overlapped\nw/ flanked TAD boundary")) +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))
```

### 2019-05-22 Scripts/evaluating_cv_metric_on_enet_penalization.Rmd
editted results scripts

>>>>

```{r}
enet_df <- readRDS("Z:/TAD_data_analysis/evaluating_cv_metric_on_enet_penalization/enet_df.rds")
enet_df$Resolution <- c(rep("10 kb", 16),
                        rep("25 kb", 16),
                        rep("50 kb", 16),
                        rep("100 kb", 16))
enet_df$Resolution <- factor(enet_df$Resolution, levels = c("10 kb", "25 kb", "50 kb", "100 kb"))
enet_df$Metric <- factor(enet_df$Metric, levels = c("ROC", "AUC", "F", "MCC"))

#alpha
all_enet_alpha <- ggplot(enet_df, aes(x=Resolution, y=Alpha, fill=Metric)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Resampling) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

#lambda
all_enet_lambda <- ggplot(enet_df, aes(x=Resolution, y=Lambda, fill=Metric)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Resampling) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

figure <- ggarrange(all_enet_alpha,
                    all_enet_lambda,
                    ncol=1,
                    nrow=2,
                    common.legend = TRUE,
                    legend = "top")
figure
```
